---
title: "The Chase"
author: "Adam J Campbell"
date: "04/09/2020"
output: html_document
---

load the packages we need.
```{r load packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(extrafont)
library(scales)

source("ETL.R")
source("custom_gg.R")
```

Rescape data if we need to.
```{r scrape data, message=FALSE, warning=FALSE}
players <- getPlayerData()
episodes <- getEpisodeData()

# save data
save(list = c("players", "episodes"), file = "ChaseData.Rdata")
```

Load data from previously scraped data
```{r load data, message=FALSE, warning=FALSE}
load(file = "ChaseData.Rdata")
```

How often are low, mid, and high offers taken
```{r message=FALSE, warning=FALSE}
offers <- players %>%
  select(c(CashBuilder,LowerOffer,HigherOffer,ChosenOffer)) %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>%
  group_by(OfferTaken) %>% 
  summarise(
    number_taken = n()
  ) %>% 
  mutate(percent = prop.table(number_taken)) 
```

Graph of average high offer and lower offer by cashbuilder
```{r message=FALSE, warning=FALSE}
plot_data <- players %>% 
    mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  ))

low_high_by_CashBuilder <- players %>%
  group_by(CashBuilder) %>% 
  summarise(
    avg_low = mean(LowerOffer,na.rm = TRUE),
    avg_high = mean(HigherOffer),
    med_low = median(LowerOffer,na.rm = TRUE),
    med_high = median(HigherOffer)
  )

ggplot()+
  geom_point(data =players, aes(x = CashBuilder, y = LowerOffer), color = "red")+
  geom_point(data =players, aes(x = CashBuilder, y = HigherOffer), color = "purple")+
  geom_line(data = low_high_by_CashBuilder, aes(x= CashBuilder, y = avg_low), color = "red")+
  geom_line(data = low_high_by_CashBuilder, aes(x= CashBuilder, y = avg_high), color = "purple")+
  geom_line(data = low_high_by_CashBuilder, aes(x= CashBuilder, y = CashBuilder))
```

Likelihood of taking high offer based on high offer 
```{r message=FALSE, warning=FALSE}
library(scales)
source("custom_gg.R")

# custom colors
my_colors = c("#207561", "#589167", "#a0cc78")

# cuts to use in bar graph
high_offer_cuts =  c(
  0, 10000, 20000, 30000, 40000, 50000, 60000, 70000, 80000, 90000, 100000, Inf)
high_offer_breaks = c("(0,1e+04]","(1e+04,2e+04]","(2e+04,3e+04]","(3e+04,4e+04]", "(4e+04,5e+04]",
                      "(5e+04,6e+04]", "(6e+04,7e+04]", "(7e+04,8e+04]", "(8e+04,9e+04]",
                      "(9e+04,1e+05]", "(1e+05,Inf]")
high_offer_labels = c("≤10k", "10-20k", "20-30k","30-40k","40-50k","50-60k","60-70k","70-80k",
                      "80-90k","90-100k",">100k")

plot_data <- players %>% 
    mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>% 
  mutate(cuts = cut(HigherOffer, high_offer_cuts)) %>% 
  group_by(cuts, OfferTaken) %>% 
  summarise(count = n())

plot_data$OfferTaken <- factor(plot_data$OfferTaken, levels = c("Higher", "Middle", "Lower"))

ggplot(plot_data, aes(fill=OfferTaken, y=count, x=cuts)) + 
  geom_bar(position="fill", stat="identity")+
  scale_fill_manual(values = my_colors)+
  scale_x_discrete(breaks = high_offer_breaks,
                   labels= high_offer_labels)+
  xlab("Higher Offer Value (£)") +
  labs(fill = "OFFER TAKEN")+
  ggtitle("How enticing is the higher offer?") +
  
  scale_y_continuous(name = "Percentage of time offer is taken", labels = percent, expand = c(-1,1) )+
  theme_campbead()
```

Compute how winning percentage for each offer taken.
```{r message=FALSE, warning=FALSE}
Total_offers <- players %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>% 
  mutate(win = ifelse(HTH_Result >0, TRUE, FALSE)) %>% 
  group_by(OfferTaken, win) %>% 
  summarise(
    total_count = n()
  ) %>% 
  ungroup() %>% 
  group_by(OfferTaken) %>% 
  summarise(
    total_total = sum(total_count)
  )

Total_offers_wins <- players %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>% 
  mutate(win = ifelse(HTH_Result >0, TRUE, FALSE)) %>% 
  group_by(OfferTaken, win) %>% 
  summarise(
    total_count = n()
  ) 

Total_offers_wins <- left_join(Total_offers_wins, Total_offers, by = "OfferTaken") %>% 
  filter(win == TRUE) %>% 
  mutate(pct = total_count/total_total)
```


Likelihood of winning HTH based on chosen value for zoomed in region.
```{r fig.height=5.5, fig.width=10, message=FALSE, warning=FALSE}
my_colors = c("#207561", "#589167", "#a0cc78")

temp_data <- players %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>% 
  mutate(win = ifelse(HTH_Result >0, TRUE, FALSE)) 

total_data <- temp_data %>% 
  mutate(ChosenOffer = round(ChosenOffer,-3)) %>% 
  group_by(ChosenOffer, OfferTaken) %>% 
  summarise(total_count = n())

ind_data <- temp_data %>% 
  mutate(ChosenOffer = round(ChosenOffer,-3)) %>% 
  group_by(ChosenOffer, OfferTaken, win) %>% 
  summarise(count = n())

plot_data <- left_join(ind_data,total_data, by = c("ChosenOffer" = "ChosenOffer", "OfferTaken" = "OfferTaken" )) %>% 
  filter (win == TRUE) %>% 
  mutate(win_pct = count/total_count)

plot_data$OfferTaken <- factor(plot_data$OfferTaken, levels = c("Higher", "Middle", "Lower"))
Total_offers_wins$OfferTaken <- factor(Total_offers_wins$OfferTaken, levels = c("Higher", "Middle", "Lower"))
plot_data <- plot_data %>% 
  filter(OfferTaken != "Higher")


plot <- ggplot() +
  geom_hline(data = Total_offers_wins, aes(color=OfferTaken, yintercept = pct), size = 0.5, show.legend = FALSE, linetype = "dotted") +
  geom_point(data = plot_data, aes(color=OfferTaken, y=win_pct, x=ChosenOffer, size = total_count)) +
  geom_text(
    data = Total_offers_wins, 
    aes(x=12000, y= pct, label = paste0(round(pct * 100,0), "%")),
    family = "Fira Mono",
    size = 3,
    position = position_nudge(y = 0.02)
    ) +
  scale_color_manual(values = my_colors) + 

  #ylim(0,1)+
  xlab("Chosen Offer (£) rounded to nearest thousand") +
  scale_x_continuous(
    breaks = seq(-6000, 12000,2000),
    limits = c(-6000,12000),
    labels = comma(seq(-6000, 12000,2000))
  ) + 
  scale_y_continuous(
    name = "Win Percentage", 
    labels = percent,  
    expand = expansion(mult = c(0.5,0.05)),
    breaks = seq(0,1, 0.20)
    ) +
  labs(color = "OFFER TAKEN", size = "TOTAL ATTEMPTS")+
  guides(colour = guide_legend(override.aes = list(size=7))) +
  theme_campbead()

plot

#ggsave("WinningPCT_Zoomed.png", plot, width = 10, height = 5.5, dpi = 300)

```


Likelihood of winning HTH based on chosen value for high offers.
```{r fig.height=5.5, fig.width=10, message=FALSE, warning=FALSE}
my_colors = c("#207561", "#589167", "#a0cc78")

temp_data <- players %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>% 
  mutate(win = ifelse(HTH_Result >0, TRUE, FALSE)) 

total_data <- temp_data %>% 
  mutate(ChosenOffer = round(ChosenOffer/5000) * 5000) %>% 
  group_by(ChosenOffer, OfferTaken) %>% 
  summarise(total_count = n())

ind_data <- temp_data %>% 
  mutate(ChosenOffer = round(ChosenOffer/5000) * 5000) %>% 
  group_by(ChosenOffer, OfferTaken, win) %>% 
  summarise(count = n())

plot_data <- left_join(ind_data,total_data, by = c("ChosenOffer" = "ChosenOffer", "OfferTaken" = "OfferTaken" )) %>% 
  filter (win == TRUE) %>% 
  mutate(win_pct = count/total_count)

plot_data$OfferTaken <- factor(plot_data$OfferTaken, levels = c("Higher", "Middle", "Lower"))
 plot_data <- plot_data %>% 
   filter(OfferTaken == "Higher")


plot <- ggplot(plot_data, aes(color=OfferTaken, y=win_pct, x=ChosenOffer, size = total_count)) +
  geom_point() +
  scale_color_manual(values = my_colors) +
  
  #ylim(0,1)+
  xlab("Chosen Offer (£)") +
  scale_x_continuous(
    breaks = seq(15000, 100000,5000),
    limits = c(15000, 100000),
    labels = comma(seq(15000, 100000,5000))
  ) + 
  scale_y_continuous(
    name = "Win Percentage", 
    labels = percent,  
    expand = expansion(mult = c(0.5,0.05)),
    breaks = seq(0,1, 0.20)
    ) +
  labs(color = "OFFER TAKEN", size = "TOTAL ATTEMPTS")+
  guides(colour = guide_legend(override.aes = list(size=7))) +
  theme_campbead()

plot

#ggsave("WinningPCT.png", plot, width = 10, height = 5.5, units = "in",  dpi = 300)

```


What is the distribution of correct answers?
```{r}
answer_distribution <- players %>%
  mutate(CorrectAnswers = CashBuilder /1000)

answer_stats <- answer_distribution %>% 
  summarise(
    players = n(), 
    total_correct = sum(CorrectAnswers),
    mean = mean(CorrectAnswers), 
    median = median(CorrectAnswers), 
    sd = sd(CorrectAnswers)
  )

ggplot(data = answer_distribution) +
  geom_bar(aes(x=CorrectAnswers), stat) +
  theme_campbead()
```

```{r}
temp_data <- answer_distribution %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  )) %>% 
  mutate(win = ifelse(HTH_Result >0, TRUE, FALSE)) 

total_data <- temp_data %>% 
  group_by(CorrectAnswers, OfferTaken) %>% 
  summarise(total_count = n())

ind_data <- temp_data %>% 
  group_by(CorrectAnswers, OfferTaken, win) %>% 
  summarise(count = n())

plot_data <- left_join(ind_data,total_data, by = c("CorrectAnswers" = "CorrectAnswers", "OfferTaken" = "OfferTaken" )) %>% 
  filter (win == TRUE) %>% 
  mutate(win_pct = count/total_count)


ggplot(data = plot_data, aes(x = CorrectAnswers, y=win_pct, color = OfferTaken, size = total_count)) +
  geom_point() +
  geom_smooth(
    method = "lm", 
    mapping = aes(color = OfferTaken, weight = total_count), 
    show.legend = FALSE) +
  theme_campbead()
```


Build model and calculate expected value for each offer


```{r}
# predicted_winning_pct <- plot_data %>% 
#   group_by(OfferTaken, ) %>% 
#   summarise(
#     value = lm(win_pct ~ CorrectAnswers)
#   )


predicted_winning_pct <- plot_data  %>%
  group_by(OfferTaken)%>%
  group_map(~ broom::tidy(lm(win_pct ~ CorrectAnswers, data = .x, weights = total_count)))

# I want to make a datatable of the structure
# Correct Answers, Offer, predicted win %

# set the sequences
Correct_Answers_seq = seq(from= 0, to= 12, by =1)
offers_seq = c("High", "Low", "Middle")

# initialise lists
Correct_Answers_list = rep(NA, length(Correct_Answers_seq) * length(offers_seq))
offers_list = rep(NA, length(Correct_Answers_seq) * length(offers_seq))
winning_model_list = rep(NA, length(Correct_Answers_seq) * length(offers_seq))

# loop over fill in values
for (i in 1:length(Correct_Answers_seq)){
  for (j in 1:length(offers_seq)){
    # set indexes
    Correct_Answers_list[(i-1)*length(offers_seq) + j] = Correct_Answers_seq[i]
    offers_list[(i-1)*length(offers_seq) + j] = offers_seq[j]
    
    temp_pct = Correct_Answers_seq[i] * predicted_winning_pct[[j]]$estimate[2] + predicted_winning_pct[[j]]$estimate[1]
    
    winning_model_list[(i-1)*length(offers_seq) + j] = temp_pct
    
  }
}

#combine lists into single data frame and rename columns
winning_model <- data.frame(Correct_Answers_list, offers_list, winning_model_list) %>% 
  #new = #old
  rename(
    CorrectAnswers = Correct_Answers_list, 
    Offer = offers_list,
    WinChance = winning_model_list
  )

```


Take the player dataframe, make longer
```{r}
player_expected <- players %>% 
  mutate(OfferTaken = case_when(
    ChosenOffer == LowerOffer ~ "Lower",
    ChosenOffer == CashBuilder ~ "Middle",
    ChosenOffer == HigherOffer ~ "Higher"
  ))#w %>%
  #pivot_longer(Name, names_to = ChosenOffer)
```

